Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and Physics

### 2020-07-13 vesicle_code/docs/permeableVes/main.tex
few changes to pnas paper

\begin{figure}[htp]
  \centering
  %\ifTikz
  %\input{figures/shearPhaseDiagramRA2.tikz}
  %\fi
  \includegraphics[width=\linewidth]{figures/shearPhaseDiagramRA2.pdf}
  \caption{\label{fig:shearPhaseDiagram} The steady state shape of a
  semi-permeable vesicle with several different permeability rates
  $\beta$ and shear rates $\dot{\gamma}$. The black lines represent
  contour lines of the final reduced areas (left) and the inclination
  angle (right). The reduced area and inclination angle of each contour
  line are reported.}
\end{figure}

@@

\begin{figure}[htp]
%  \ifTikz
%  \input{figures/parabolicPhaseDiagram.tikz}
%  \fi
  \includegraphics[width=0.8\linewidth]{figures/parabolicPhaseDiagram.pdf}
  \caption{\label{fig:parabolicPhaseDiagram} The steady state shape of a
  semi-permeable vesicle with several different permeability rates
  $\beta$ and flow rates $U$. At high flow rates, the vesicle
  self-intersects before reaching a steady state configuration.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in Stenosis}
Inspired by an experiment that measured the effects of cells on the
dynamical pressure-drop variations along a micrometer-sized
channel~\cite{abk-fai-sto2006}, we consider a numerical experiment where
a semi-permeable vesicle passes through a constriction. We also measure
the pressure-drop variation by measuring the pressure at the inlet and
outlet of the constriction.

In each experiment, we initialize an elliptical vesicle with longest
diameter of 9$\mu$m. We use a length scale of $R_0 = 10^{-6}$m, a
bending stiffness of $k_b = 10^{-19}$J, and fluid viscosity of $\mu=5
\times 10^{-2}$kg/ms. Using the relaxation time scale $\tau = \mu
R_0^3/k_b = 5 \times 10^{-1}$s, the velocity scale is $U = 2 \times
10^{-6}$m/s, and the pressure scale is $P = k_b/R_0^3 = 10^{-1}$Pa.  The
geometry is similar to the experiment~\cite{abk-fai-sto2006} where the
membrane starts in a channel with diameter $25\mu$m and passes into a
channel with length $45\mu$m and diameter $5\mu$m. Our numerical methods
are unable to achieve the high-speed flow rate in the experiments, so we
consider a much smaller flow rate.

\begin{figure}[htp]
%  \ifTikz
  \input{figures/stenosisGeom.tikz}
%  \fi
%  \includegraphics[width=0.8\linewidth]{figures/parabolicPhaseDiagram.pdf}
  \caption{\label{fig:stenosisGeom} A caption.}
\end{figure}

@@

 \newpage
\input{figures/shearPhaseDiagramRA2.tikz}
%\input{figures/parabolicPhaseDiagram.tikz}

>>>>

\begin{figure}[htp]
  \centering
  %\ifTikz
  %\input{figures/shearPhaseDiagramRA2.tikz}
  %\fi
  \includegraphics[width=0.9\linewidth]{figures/shearPhaseDiagramRA2.pdf}
  \caption{\label{fig:shearPhaseDiagram} The steady state shape of a
  semi-permeable vesicle with several different permeability rates
  $\beta$ and shear rates $\dot{\gamma}$. The black lines represent
  contour lines of the final reduced areas (left) and the inclination
  angle (right). The reduced area and inclination angle of each contour
  line are reported.}
\end{figure}

@@

\begin{figure}[htp]
%  \ifTikz
%  \input{figures/parabolicPhaseDiagram.tikz}
%  \fi
  \includegraphics[width=0.9\linewidth]{figures/parabolicPhaseDiagram.pdf}
  \caption{\label{fig:parabolicPhaseDiagram} The steady state shape of a
  semi-permeable vesicle with several different permeability rates
  $\beta$ and flow rates $U$. At high flow rates, the vesicle
  self-intersects before reaching a steady state configuration.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in Stenosis}
Inspired by an experiment that measures the effects of cells on 
dynamical pressure-drop variations along a micrometer-sized
channel~\cite{abk-fai-sto2006}, we consider a numerical experiment where
a semi-permeable vesicle passes through a constriction. We also measure
the pressure-drop variation by measuring the pressure at the inlet and
outlet of the constriction.

In each experiment, we initialize an elliptical vesicle with longest
diameter of 9$\mu$m. We use a length scale of $R_0 = 10^{-6}$m, a
bending stiffness of $k_b = 10^{-19}$J, and fluid viscosity of $\mu=5
\times 10^{-2}$kg/ms. Using the relaxation time scale $\tau = \mu
R_0^3/k_b = 5 \times 10^{-1}$s, the pressure scale is $P = k_b/R_0^3 =
10^{-1}$Pa. The geometry is similar to an
experiment~\cite{abk-fai-sto2006} where the membrane starts in a channel
with diameter $25\mu$m and passes into a channel with length $45\mu$m
and diameter $5\mu$m (Figure~\ref{fig:stenosisGeom}. We impose a
Poiseuille flow at an inlet and outlet and a no-slip boundary condition
on the upper and lower walls. The flow rate is chosen so that the
residency time of the vesicle in the constriction agrees with the
experimental results.

\begin{figure}[htp]
%  \ifTikz
  \input{figures/stenosisGeom.tikz}
%  \fi
%  \includegraphics[width=0.8\linewidth]{figures/parabolicPhaseDiagram.pdf}
  \caption{\label{fig:stenosisGeom} A caption.}
  \todo[inline]{Put snapshots of configuration in the geometry}
\end{figure}

\begin{figure}[htp]
%  \ifTikz
  \input{figures/stenosisPressureFluctuation.tikz}
%  \fi
  \caption{\label{fig:stenosisPressure} The excess pressure across the
  constriction in Figure~\ref{fig:stenosisGeom}. The black dashed lines
  denote the start and end of the constriction. The results are
  qualitative agreement with~\cite{abk-fai-sto2006}.}
\end{figure}

@@

% \newpage
%\input{figures/shearPhaseDiagramRA2.tikz}
%\input{figures/parabolicPhaseDiagram.tikz}
